### 2015-07-08 paper.tex
optimize the part: A promising secondary trigger system design and add a picture

		With the reconstructed approximate vertex, we can
		set different radius threshold to reduce radioactivity
		backgrounds. In the trigger system, the first and secondary trigger system are in parallel. 
		In the first trigger system, we record the events which the visible energy
		greater than energy threshold. In the secondary trigger system, 
		we record the events which the visible energy less than energy threshold 
		and the reconstructed vertex position less than radius threshold.
		In table.2 we show the central detector's sum radioactivity background rate
		on different energy and radius threshold.

@@

		\section{The event rate estimation of water pool}

		\section{The event rate estimation of top tracker}

>>>>

		We simulate the low energy C14 event and give the delta of true event vertex and 
		the reconstructed approximate event vertex in Fig.5.

		\begin{center}
			%\includegraphics[width=6cm]{acrylicoption.png}
			\includegraphics[width=7cm]{C14_deltaR.png}
			\figcaption{\label{fig2}   Delta of true C14 event vertex and reconstructed approximate event vertex}
		\end{center}

		Form Fig.5, we can see the error of reconstructed event vertex is less than 5 meter. 
		With the reconstructed approximate vertex, we can
		set different radius threshold to reduce radioactivity
		backgrounds. In the trigger system, the first and secondary trigger system are in parallel. 
		In the first trigger system, we record the events which the visible energy
		greater than energy threshold. In the secondary trigger system, 
		we record the events which the visible energy less than energy threshold 
		and the reconstructed vertex position less than radius threshold.
		In table.2 we show the central detector's sum radioactivity background rate
		on different energy and radius threshold.

@@

		\section{Conclusion}
